\section{Main Functionalities}
%What are the main functionalities of the web app? what services does it offer and how it is organized?

Our web application defines a Fitness Tracker, capable of managing the creation of your personal account, save your exercises schedule with the possibility of adding a description to keep track of your progress.
It also allows you to manage your diets with the possibility of creating one or more personalized ones or simply uploading those from your nutritionist.
Other important features are meal management, the analysis of your personal statistics with graphs to show your progress(weight loss or gain) and the possibility of communicating in a dedicated forum with the aim of helping and bringing closer to this world the novices.








In particular, our Web Application is divided in 6 main parts:
\begin{itemize}
    \item User Management: Users can register, login and visualize/modify his personal information. 
    \item Statistics Management: User's Collected data are used to generate an overview of their progress in both Gym and Diet areas. 
    \item Social Network Management: User can make a post, made of text and eventually an image, expressing his gym progress, his current diet or anything else he want. User can also like and comment other users post. An home page will show all the posts with related likes and comments. 
    \item Diets Management: Users can view their diet plans or add multiple ones ensuring the possibility of keeping track of what you have to eat each day.
    \item Meals Management: Users can view what they ate, can register their meals and can register new foods.
    \item Exercises Management: Users can see their exercise plans or add their own exercise plans , modify them or remove them.
    
   
\end{itemize}